Incentivizing Exploration by Heterogeneous Users

### 2018-06-06 problem_setting.tex
clarified discrete nature

Assumption~\ref{A1} implies that ties happen with probability $0$.
One special case of interest we discuss below is
$\TieDensity = 0$. This case arises when there is a cutoff
\TieCutoff such that only a measure-zero set of agents has two best arms
within utility \TieCutoff of each other.
In particular, $\TieDensity = 0$ happens whenever \AgentDist is discrete,
i.e., supported on a finite set of types,
and each type has a unique best arm.

>>>>

Assumption~\ref{A1} implies that ties happen with probability $0$.
One special case of interest we discuss below is $\TieDensity = 0$.
This case arises when there is a cutoff
\TieCutoff such that only a measure-zero set of agents has two best arms
within utility \TieCutoff of each other.
In particular, $\TieDensity = 0$ happens whenever \AgentDist is \dkdelete{discrete,
i.e.,} supported on a finite set of types,
and each type has a unique best arm.
